---
title: "Untitled"
author: "vishnu sagar2021"
date: "2/4/2021"
output: html_document
---
#Assignment
1. Read the dataset from ....
```{r}
data1=read.csv("/cloud/project/Assignment01_data/government-finance-statistics-general-government-year-ended-june-2020-csv.csv", sep = ",", header = T, na.strings = "NA", stringsAsFactors = F,dec = ".")

data1

#charecter variables, convert them to factors in the next step : Ans: stringsAsFactors = T
data2=read.csv("/cloud/project/Assignment01_data/government-finance-statistics-general-government-year-ended-june-2020-csv.csv", sep = ",", header = T, na.strings = "NA", stringsAsFactors = T,dec = ".")
data2

#Show the data is read properly by printing first few rows.
head(data2)

```

#2. Create a 3*3 matrix A using the following data [4,5,7,8,0,9,5,4,8]. Find the transpose of the matrix.
```{r}
matrix_A= matrix(c(4,5,7,8,0,9,5,4,8), nrow = 3, ncol = 3, byrow = TRUE)
matrix_A
#Find the transpose of the matrix.
t(matrix_A)

```
#3. Create a 3*3 matrix B using the following data [14,52,75,89,10,91,51,44,28]. Using matrix A and B find A + B, A - B and A*B.

```{r}
matrix_A= matrix(c(4,5,7,8,0,9,5,4,8), nrow = 3, ncol = 3, byrow = TRUE)
matrix_A
matrix_B=matrix(c(14,52,75,89,10,91,51,44,28), nrow = 3, ncol = 3, byrow = TRUE)
matrix_B

#sum of Matrix
sum= matrix_A+matrix_B
sum
#subtraction
sub= matrix_A-matrix_B
sub
#multiplication
prod= matrix_A*matrix_B
prod
```

#Create 2 vectors with 7 elements each and perform all the vector operations.

```{r}
vector1=c(2,4,6,8,10,12,14)
vector2=c(3,5,7,9,11,13,15)
typeof(vector1)
typeof(vector2)

class(vector1)
length(vector1)
str(vector1)
vector3= as.character(vector1)

sum=vector1+vector2
sum

```
#5. Create the following vectors and create a data frame using those vectors. Also find the charectristics of the data frame.
id,name,salary,start_date,dept
1,Rick,623.3,2012-01-01,IT
2,Dan,515.2,2013-09-23,Operations
3,Michelle,611,2014-11-15,IT
4,Ryan,729,2014-05-11,HR
5,Gary,843.25,2015-03-27,Finance
6,Nina,578,2013-05-21,IT
7,Simon,632.8,2013-07-30,Operations
8,Guru,722.5,2014-06-17,Finance

```{r}
id= c(1:8)
name= c("Rick","Dan","Michelle","Ryan","Gary","Nina","Simon","Guru")
salary= c( 623.3,515.2,611,729,843,578,632,722.5)
start_date= as.Date(c ("2012-01-01", "2013-09-23","2014-11-15","2015-03-27","2013-07-30","2013-07-30","2013-07-30","2013-07-30"))
dept = c("IT", "Operations", "IT","IT", "Operations", "IT","IT")


salary_data= data.frame (c(1:8),
name= c("Rick","Dan","Michelle","Ryan","Gary","Nina","Simon","Guru"),
salary= c(623.3,515.2,611,729,843,578,632,722.5),
start_date= as.Date(c("2012-01-01", "2013-09-23","2014-11-15","2015-03-27","2013-07-30","2013-07-30","2013-07-30","2013-07-30")),
dept = c("IT", "Operations", "IT","IT", "Operations", "IT","IT","IT"),
stringsAsFactors = FALSE)
salary_data


```

