---
title: "R_packages day 10"
author: "vishnu sagar2021"
date: "2/2/2021"
output: html_document
---
#R data interfaces
In R, we can read data from files stored outside the R environment./
We can also write data into files which will be stored and accessed by the operating system./
R can read and write into various file formats like csv, excel, xml etc./
## Getting and Setting the Working Directory
Check which directory the R workspace is pointing to using the `getwd()` function./
Set a new working directory using `setwd()` function./

```{r}
getwd()
setwd("/cloud/project")
print(getwd)
```
#input the data as csv file

sample, ph, DO, BOD\
1, 7, 4, 2\
2,6.5, 3.6,3.2\
3,5.9, 4.2,2.1\
4, 5.7.4.4, 1.9\
reading csv files
read.csv()
`read.csv(file, header = TRUE, sep = ",", quote = "\"", dec = ".", fill = TRUE, comment.char = "",  na.strings = "NA", strip.white = TRUE, stringsAsFactors = FALSE)`

```{r}
data=read.csv("", sep= ",", dec= ".", header = "T", stringsAsFactors = F, fill = "T")
read.csv 

```



```{r}
install.packages(https://cran.r-project.org/doc/manuals/r-patched/R-admin.html#Installing-packages)
any(grepl("xlsx",installed.packages("xlsx")))

library("xlsx")

search("xlsx")
search()
any(grepl("xlsx",installed.packages("xlsx")))
data= read.xlsx ("/E/Kerala University/online class/data_model",password = password, sheetIndex = 1)

setwd ("xlsx")

```
```{r}

library("xlsx", lib.loc = "path to library")

data= read.xlsx ("/E:/Kerala University/online class/data_model",password = password, sheetIndex = 1)
```

